---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
[![Build Status](https://travis-ci.org/alan-y/objectremover.svg?branch=master)](https://travis-ci.org/alan-y/objectremover)
[![](https://cranlogs.r-pkg.org/badges/objectremover)](https://cran.r-project.org/package=objectremover)

# objectremover

`objectremover` is an RStudio addin to assist with clearing objects from the Global environment. Features include removing objects by

* Starting pattern of object name
* Ending pattern of object name
* Regular expression
* Object type (dataframe, function and other)

## Installation
Install `objectremover` with

```{r install, eval = FALSE} 
install.packages("objectremover")
```

Alternatively, you can install the development version of `objectremover` with

```{r install_devel, eval = FALSE} 
devtools::install_github("alan-y/objectremover")
```

## Use

After installing the package, the add-in will be available in Rstudio from the **Addins** dropdown menu. Select "Remove Objects" (under the heading OBJECTREMOVER) from the menu to run.
